\section{Analysis of Wilson Hicks: ``What is Photojournalism?''}

Hicks occupied a position that gave him a substantial amount of authority on
photojournalism; he contributed to the medium in a way that made him a witness
to the evolution of photojournalism, just as the photojournalist was a witness
to news stories. That said, it also put him in a position of power as a
firsthand reporter on something he helped to create. Overall, he writes in
concrete, absolute statements, often presenting questions or counter-arguments
immediately after his point and then addressing them---an apt reflection of his
position as the journalist of photojournalism.

To address the question he posed in his title, Hicks breaks the problem down
into two approaches: first, he defines photojournalism from within by excising
its components and asserting how each segment functions as part of the whole
medium; second, he describes photojournalism externally by providing an overview
of the social and technological developments worldwide that needed to occur in
order for photojournalism to have a place. Both approaches are necessary for a
complete statement on an otherwise complicated medium with many variables and
expectations; the initial technical definition comes first as a foothold for the
reader to understand the social structure that comes second.

By Hicks's technical definition, photojournalism is a combination of words and
pictures; more directly, it is one unit of expression that affects both the eyes
and the ears of the reader (words, he states, as a means to stimulate the ears,
and pictures to stimulate the eyes). This unit combines with what he calls the
`X-factor'---the ideas, memories, and beliefs carried by the reader---in order
to form an experience that is greater than what each of the three segments could
have provided alone. With this, then, the existence of an audience is crucial to
the success of Hicks's photojournalism. In the production of photojournalism, he
ascribes each piece to a separate role: the writer, the photographer, and the
editor, that even if one person holds multiple roles, all three must exist in a
balanced, cohesive group in order to achieve success.

Additional to the three segments of a unit of photojournalism, Hicks
deconstructs how the photograph itself contributes to the experience. He points
out that in reality, human vision is limited, affected by the mind's capacity to
observe and process imagery; the camera, in that sense, has a superior
perception of the visual world, able to mechanically record images without the
burden of emotions. Furthermore, photographs gave people the ability to examine
an image free of the immediacy of reality, and thus allows the formation of a
new sort of emotional response not previously possible. It's this particular
power of photography that Hicks claims as a major contributor to the success of
photojournalism.

In tracing the social trajectory of photojournalism, Hicks attributes the
turning point to the technological advancements offered by the Leica, a camera
that was so small and unobtrusive compared to previous machines. Previously, the
presence of a camera unavoidably changed events due to the physical intrusion of
a camera and all its related entourage, but once the actual act of photography
was simplified, entirely different photographs were possible---rapid sequences,
low light, and less arranged shoots, to name a few. Coupled with the ability to
distribute photographs in print media, photographs became a more integrated part
of journalism, rather than just an illustrative or design element to accompany
text. With the Leica, photographers were able to speak to the point that Hicks
makes about why photography is effective: the non-intrusive images showed scenes
that viewers could interpret as if they were there, but without the problems of
faulty perception and memory. Additionally, photographers themselves could hone
and rely on their instincts for capturing images with the potential to have this
effect.

The interesting part about Hicks's account of the development of
photojournalism, specifically with regards to \textit{Life}, is that his syntax
does not give away, or even imply, that he was involved heavily with its
production. However, the breadth of detail and absolute descriptions give a
sense of witness to that development; it's as if he wanted to see
photojournalism in the way that the camera saw events, with the ability to
record and not judge. That said, the selectivity of the camera applied to
Hicks's position as well; the more absolute his statements, the narrower a path
he must take, and his perspective did not allow intrusions beyond the
definitions he carefully laid out.
