\begin{description}
    \item [79-346 American Political Humor from Mark Twain to the Daily Show]
        This course takes a cultural approach to U.S. history since the Civil
        War, as seen by the nation's most astute and influential critics: its
        political humorists. Besides immortals like Mark Twain and contemporary
        novelist Don DeLillo, we will (re)discover the satirical yet hilarious
        voices of H.L. Mencken, Will Rogers, Dorothy Parker, Walt ``Pogo''
        Kelly, Richard Pryor, Fran Lebowitz, and others through essays, novels,
        recordings and films. Throughout the term, we will collaborate in
        defining terms and learning a vocabulary we can use to discuss and write
        analytically about ephemeral, topical critiques that make us laugh in
        order to make us think. How does ``humor'' differ from ``comedy'' or
        from ``jokes''? Beyond lampooning government or elections, what makes
        humor ``political''? What are the relationships between politics and
        art?  What can political humor reveal that we might not ``get'' by any
        other means?  At its sharpest edges, humor addresses issues of class,
        gender and race in American life, and provokes alternative thinking
        about mass culture, consumerism, and conformity. To provide context and
        analytical resources for these themes, we will also read historical
        studies and relevant theories by Sigmund Freud, Luigi Pirandello, and
        Mary Douglas.  Assignments include four analytical essays, entries in a
        collaborative online glossary, a brief oral report, and occasional short
        quizzes on assigned readings.
    \item [79-316 Trajectories in Photography: Prehistory to 1945] This course
        explores how photography influenced and was shaped by social and
        political changes in the 19th and early 20th centuries. We will
        investigate photography in its modern and modernist constructions, with
        special attention to both continuities and ruptures between the
        pre-modern and the modern. Specific topics will include: the nature of
        pictures and precedents in picture-making, from cave paintings through
        20th-century experiments in photography; photography's role in the
        rationalization of geographies and peoples; the promises of photography
        as a new technology alongside electricity and the motion picture; the
        position of photography in relation to fine art; publications, mass
        media and propaganda; social photography, documentary photography and
        activist photography; and vernacular photography and photography's
        popular uses. The course draws from various disciplinary perspectives
        including art history, anthropology, history, and science and technology
        studies. The course will include instructor lecture, student
        presentations, and guest lecturers. Class discussion will be an integral
        aspect of the class.
    \item [79-212 China and Its Neighbors: Minorities, Conquerors, and Tribute
        Bearers] This course examines East Asian peoples on the periphery of the
        Han Chinese and their interrelations from the time of Genghis Khan to
        the present, including Mongols, Manchus, Koreans, Tibetans, Muslim Turks
        of Central Asia, and ethnic groups of south China. It is, in part, a
        history of a civilization seen from its margins. We question the usual
        narrative of Chinas uncomplicated absorption of its neighbors and
        conquerors, and pay attention, unconventionally, to voices of minority
        peoples. Besides ecology, war and diplomacy, we examine cultural
        conceptions and mutual influences. We also look for the emergence of a
        sense of identity among peoples in contact, including Han Chinese,
        especially at the onset of nationalism and industrialization. The course
        also looks at some Western views of the subcontinents peoples.
    \item [79-245 Capitalism and Individualism in American Culture] This small
        discussion course traces ideas about individualism and capitalism in the
        U.S., from colonial times to the present. We will focus on three main
        themes: 1) the relationship between capitalism, work, and identity; 2)
        changing definitions of success and failure; and 3) the historical
        origins of contemporary attitudes toward 1 \& 2. In short, we will study
        the economics and emotions of the American dream: how class, race,
        gender, occupation, and ambition shape our identities.  Readings include
        ``The Autobiography of Benjamin Franklin,'' studies by Alexis de
        Tocqueville and Max Weber, writings of Frederick Douglass, Ralph Waldo
        Emerson, Herman Melville, and Henry Thoreau, Kate Chopin's ``The
        Awakening,'' Andrew Carnegie's ``Gospel of Wealth,'' Arthur Miller's
        ``Death of a Salesman,'' and other works. Grading is based upon a
        readings journal, participation in discussion, three short essays and a
        longer final paper.
    \item [79-262 Modern China] Assuming no prior familiarity with China or its
        culture, this course examines China's continuous changes from the 1800s
        on, in its cultural traditions, identities, daily life, social
        relations, and self-perceptions, engendered by both internal initiatives
        and external contact. We look at how changes unfolded in mass movements
        and in individual lives, in statecraft thought and in societal
        practices. We examine the roles of such historical actors as the
        extended family, modern reformers, the state, the parties and ethnic
        groups. Participants learn to use primary sources in making historical
        observation and to critique some analytical approaches to modern Chinese
        history. Since we rely heavily on assigned readings, active class
        participation is essential in this course.
    \item [79-375 China's Environmental Crisis] In the context of China's
        changing ecology, this course explores whether and how sustainable
        development has been, is being, and might be pursued by its vast
        population and political leadership. Without neglecting culture--e.g.,
        Confucian, Daoist, Buddhist and Altaic (steppe) views of ideal
        human/environment interaction--we trace historical demographic patterns
        and their effects on China's fauna and flora, and investigate past
        government efforts at water control, migration, new crop introduction,
        natural disasters, etc. Over half of the course concerns the People's
        Republic (1949-), paying special attention to birth control policies,
        the steppe reclamation, the Three Gorges dam, industrial growth,
        pollution scandals, tourism and environmental policy. We work mostly by
        discussion, centering on materials read in advance by class members.
    \item [79-317 Art, Anthropology, and Empire] This seminar will explore the
        anthropology and history of aesthetic objects, as they travel from
        places considered ``primitive'' or ``exotic,'' to others deemed
        ``civilized'' or ``Western.'' First, we will consider twentieth-century
        anthropological attempts to develop ways of appreciating and
        understanding objects from other cultures, and in the process to
        reconsider the meaning of such terms as ``art'' and ``aesthetics.'' Then
        we will discuss several topics in the history of empire and the
        ``exotic'' arts, including: the conquest, colonization and appropriation
        of indigenous objects; the politics of display and the rise of museums
        and world fairs; the processes by which locally-produced art objects are
        transformed into commodities traded in international art markets; the
        effects of "exotic" art on such aesthetic movements as surrealism, etc.;
        and the appropriation of indigenous aesthetic styles by ``Western''
        artists. Finally, we will consider attempts by formerly colonized
        populations to reclaim objects from museums, and to organize new
        museums, aesthetic styles, and forms of artistic production that
        challenge imperialism's persistent legacies.
\end{description}
