\section{The Greyness of Mark Twain}% (revision)}

\textit{4 October 2012}

It is a tempting and simple instinct of humans to divide the world into a series
of dichotomies; truth and lies, civilized and savage, sin and morality, black
and white. However, it is the spectrum between, the infinite divisibility of the
grey area, that is worth studying. The extremes only exist as notions, ideals
that can never be realized, for one requires the context of one side in order to
note the existence of the other. Acknowledgment of both reveals a vast and
muddled space between, in which travel becomes possible and the hypocrisy of
dichotomies can be seen. Throughout his life, Mark Twain embarked on his own
journey through this inexplicable grey area, and his discoveries formed the
basis of his humor.

In ``The Importance of Mark Twain'', Alan Gribben defines Twain as the
quintessential American humorist, noting that he exists as a ``crucial
continuity'' and a ``common denominator of what we want to perceive to be the
American character''\footnote{Gribben, 48}. Indeed, Twain's status in history stands as
an almost mythological figure, a strange life bookended by two appearances of an
astrological phenomenon. Charles Neider describes him as a living incongruity,
both a clown and a tragedian, both an amateur and a competent professional, both
an optimist and a pessimist\footnote{Neider, xv}. Twain's inexplicable connection to both
the darkness and the light of the world, an intimate understanding of the
existence of dichotomies, allowed him to display the gradient of greys as he
dilutes light with darkness and vice versa.

Twain's entry into mass publication with an editorial to \textit{The Buffalo
Express} shows his curiosity of the grey field from the start. In
``Salutatory'', he provides the paper's readership with a list of absolutes,
such as confining himself to truth, rebuking all forms of crime, refraining from
vulgar speech, etc. except when he won't\footnote{ibid., 1}. This is his initial
declaration to the literate public at large, his claim that he will not be
adhering to canonically accepted notions of custom and  law. In this early
period of his life, he has already accepted the grey area that will become the
color of his future writings; he starts with the clean light that characterized
publications before him, that ``custom is law, and custom must be
obeyed''\footnote{ibid., 1} and immediately rejects it by adding a little bit of
darkness, pushing his position into issues concerning the space between.

Before he really settled into his position of writing from the grey, Twain
studied other figures that appeared in a state of incongruity. He displayed a
certain fascination with the late King Kamehameha V when he wrote ``The Sandwich
Islands''. There, he outlined the existing dichotomies of Catholic versus
heathen, civilized versus savage, the incoming whites versus the existing
natives. With those categories of light and darkness established, he then
immediately showed his appreciation for Kamehameha's ability to move between
them, how he could ``converse like a born Christian gentleman'' and then
``retire to a cluster of dismal little straw-thatched native huts by the
sea-shore, and there for a fortnight he would turn himself into a heathen whom
you could not tell from his savage grandfather''\footnote{ibid., 25}. Twain's
tone is a bit whimsical, almost envious, of Kamehameha's flexible and confusing
status; he wrote with obvious distaste and sadness that such a place would be
annexed by America, through a process that was seemingly bringing the ``lamp of
light'' into the darkness\footnote{ibid., 28}. In reality, Twain found that
something to be ridiculed, as he sarcastically exclaimed, ``We can give them
lectures! I will go myself''\footnote{ibid., 28}. He saw the imperialistic act
of assimilating and westernizing the natives as a destruction of culture; rather
than criticize it outright, though, he pretended to support the cause with this
exaggerated speech that more effectively showed his alarm.

William Keough portrays the particularly American humor that Twain frontiered as
a more violent, caustic sort than that of other cultures. Violence, however,
exists on a more basic human level than humor; it is the force that ends life
while love is the act that creates it, and humor is a response to both. Using
humor to address brutality is a way of reducing the darkness of it, bringing it
into the grey field so that it can be more easily viewed in a context with
contrast. Twain addressed a ``Person Sitting in Darkness'' from the position of
one who occupies the grey area; he did not write from the lofty tone of one who
would banish the darkness entirely by shining the full power of the sun into the
shadows, nor does he wish to snuff out the light entirely by covering it with
overwhelming shadow. Rather, he straddled the middle, addressing both the voice
of light and the listener in the dark.

``To the Person Sitting in Darkness'' is a bitter essay, one that can hardly be
considered humorous so much as it merely contains some elements of humor.
Sarcastic comments directed towards Reverend Ament, for example, ``the right man
in the right place''\footnote{ibid., 284} serve to muddy the normally pure white
image of a man of the cloth; at the same time, sympathetic speech to the
listeners in the dark, ``too scarce and too shy''\footnote{ibid., 286}, bring
them out of the darkness in which they have otherwise been placed. He levels the
playing field for them by causing both sides to exist in the same field of grey,
one that allows a closer relatability once they are all just humans in the world
together rather than strict representations of darkness and light.

The core of this essay is an identification of dichotomies, which highlight the
hypocrisy that occurs when one attempts to adhere to them; his Person Sitting in
Darkness begins to learn of the incongruities that Twain denigrates when two
kinds of Civilization are pointed out, an externally displayed one, ``strictly
for Export'', and an ``Actual Thing that the Customer Sitting in Darkness
buys''\footnote{ibid., 287}. The Person is given a voice of his own once he
starts to describe the incongruities of so-called civilized societies ``with its
banner of the Prince of Peace in one hand and its loot basket and butcher knife
in the other''\footnote{ibid., 289}. The Person continues to ponder such things
for Twain, noting that it is ``curious and unaccountable. There must be two
Americans; one that sets the captive free and one that takes a once-captive's
new freedom away from him, and picks a quarrel with him with nothing to found it
on''\footnote{ibid., 291}. Twain's ultimate point is that so long as such
dichotomies exist, there will be incongruities, as it is impossible for man to
remain firmly in either absolute state.

The essay's harsh dissection of America's habit of violently conquering native,
heathen people comes to a conclusion that is explained to the person; in
particular, he states that ``we have debauched America's honor and blackened her
face before the world''\footnote{ibid., 295}. America has been made a muddied
grey through its violent actions, bringing the country into a hypocritical and
ironic state that is ripe for Twain's humor to feed upon. The joke is that there
isn't a joke, but couched in Twain's sarcastic tone, the mixing of black and
white becomes an object of ridicule, a situation that necessitates a humorous
interpretation in spite of itself.

Once he travels too far into the darkness, Twain begins to lose his edge of
humor. In ``The Damned Human Race'', he writes almost entirely from the dark,
reaching a point in his travel across the grey space from which he does not see
a recovery for mankind. He declares that ``Man cannot claim to approach even the
meanest of the Higher Animals'', and ``constitutionally afflicted with a Defect
which must make such approach forever impossible, for it is manifest that this
defect is permanent in him, indestructible, ineradicable''\footnote{DeVoto,
228}. By both placing man in an unrecoverable darkness and situating himself in
a position that no longer acknowledges the grey area, he wrote a piece that does
not provide or a way out, nor any sympathy for humanity. In this, the absence of
humor is apparent.

To examine Twain's spectrum of writing is to see a full range of the grey
spectrum, from his early pieces that add subtle amounts of greyness in order to
give some contrast to the world of dark and light absolutes, to essays that
spell out the grey area entirely, and the final darkness of his later writings
that stand as the opposite to his initial editorials. The parts of humor that
are visible are ones where the grey area is clearly visible, when both the dark
and light boundaries can be seen, and an occupation of the grey space is the
only position from which that view is possible.
