\section{A Culture of Disunity}

\textit{3 March 2014}

As a nation with an expansive territory, China's borders contain a necessarily
diverse collection of cultures. This presents obvious difficulties for creating
and maintaining a unified state; the further from China's geographical and
cultural center, the more complicated this issue becomes. The Uyghurs and the
Mongols are very different groups, both in their semantic distinctions from the
Han center and their syntactic differences as ethnic groups.  However, they have
the shared experience of being peripheral groups that have undergone policies
and reforms instituted by the Chinese government in an attempt to bring them
under a unified national identity. How either group responded to this force of
change depended on their respective cultural backgrounds.

The geography of the Mongol region favored the development of communal,
migratory societies. Harsh steppe landscape meant a delicate ecology, with
grasslands that were prone to damage from overgrazing and erosion. As a result,
the Mongol lifestyle followed an annual migration pattern that allowed them to
raise livestock carefully without causing great disruption to the land. This
necessitated a strong community spirit and awareness of the overall health of
the region, which promoted bonds across the steppes that solidified the Mongol
identity. In spite of their mobile lifestyle, the Mongol social structure
developed as collaborative and homogeneous once they achieved a unified state.

In addition to geography, the symbolism of Chinggis Khan throughout history
contributed to the collective Mongol identity.  Almaz Khan describes this as
``one of the basic identity symbols for both the Inner and Outer
Mongols''\footnote{Khan, 248}. He goes on to trace the early period of the
region, when there did not yet exist a strong sense of Mongol unity, until
Chinggis Khan's invocation as a revered ancestor of the people in the region
served as a way to legitimize the claims of power among different
tribes\footnote{ibid., 252}. In more modern times, Chinggis Khan represents the
Mongol people's struggle for status within the Chinese state; it exists both as
a common thread of identity for the Mongols themselves, and as an object that
the central government either revered or suppressed depending on its
relationship with minority cultures\footnote{ibid., 267}.

Regardless of how Chinggis Khan has been utilized to represent the Mongols, the
important thing to note is that such a symbol exists at all; the existence of a
commonly-accepted cultural hero speaks to the existence of a commonly-accepted
cultural identity. Without that identity, there would be no hero. The strength
of such a symbol feeds into the strength of the ethnic consciousness, and vice
versa. So long as the symbol of Chinggis Khan existed, the Mongols were able to
relate to a sense of unity springing from a single foundational icon of their
history, no matter how the mythology of that icon was treated.

Regarding the Uyghurs, such a united identity did not exist prior to the PRC
designation of the Uyghur ethnic group. The Xinjiang region is mainly
uninhabitable desert, across which travel is a great hardship.  Settlements
flourished around individual oases, which could more easily sustain life;
communication to other oases occurred less frequently the longer the distance.
Social and family groups remained very tightly bound to local areas, as pride
for one's home oasis came from the practical matter of survival; without a
large, geographically close network of connections, one was unlikely to prosper.
Due to the distances between oases, trade and cultural mixing happened more
often across the border into neighboring countries than within the Xinjiang
region\footnote{Rudelson, 40}.

Due to such disparate cultural values and isolated communities, the Uyghurs
never felt a sense of unity with other people called Uyghurs. Even as the
Uyghurs must address their unavoidable status as a people united under the
Chinese designation, they still found difficulty reconciling their disparate
histories, and maintained loyalties to their home oases above their connection
to the idea of a larger ethnic group\footnote{ibid., 143}. In addition to the
problems of cross-oases identities, the Uyghurs experienced distinction between
classes that presented even stronger disconnects of cultural values and
self-identity. The intellectuals considered themselves as Turks before any other
group, the merchants as pan-Chinese, and peasants as Muslims\footnote{ibid.,
118}. Most notably, no group considered themselves primarily Uyghur, the term
that the Han assigned to all three groups.

With the lack of a homogenous identity, the Uyghurs also have not maintained a
common cultural hero. Rudelson identifies a number of historical figures that
have maintained some status as Uyghur cultural heroes, but none of them managed
to take hold of a universal position as something all the Uyghurs identify with.
The poet Abdukhaliq ``Uyghur'' mostly resonated with intellectual
nationalists\footnote{ibid., 145}, eleventh-century scholar Mahmud Qasqari
represented thestrong Islamic identity among the Uyghurs\footnote{ibid.,
153}, the former Xinjiang leader Saypidin Azizi fell out of favor with the
majority of Uyghurs for sympathizing too much with the Han\footnote{ibid., 155}.
Even if one particular figure received heavy support from one group during one
period, the disparity between the self-identification of each group resulted in
highly polarized responses across the region.

Thus, as individual ethnic groups, the Mongols and the Uyghurs differ not only
in the specifics of their language and cultural values, but also in how they fit
into the syntax of their designation as ethnic groups. Most notably, the Mongols
present a more homogenous identity, while the Uyghurs span multiple groups of
people who are not yet able to relate to each other under a common identity. In
part, this is owed to the relatively new status of the Uyghurs as one designated
group, as the Mongols were similarly scattered before they were unified under
Chinggis Khan. However, the syntactical differences of the two groups provided a
logistical challenge for the Han, whose unification policies toward ethnic
minorities seemed to assume a universal and homogenous application.

\hrulefill

As part of establishing a system of minority unification, the Chinese central
government developed an educational system to both preserve ethnic boundaries
and enforce national unity. A national standard education in such a diverse
country has two major boundaries to overcome: linguistic variance, and cultural
incompatibility. To address those boundaries, primary education in areas with a
high population of ethnic minorities included language-specific schools meant to
enforce the usage of Mandarin as the standard language for the Chinese
nation\footnote{Borchigud, 282}, and study programs emphasizing the values and
histories of the Han people\footnote{ibid., 293--294}. They also allowed special
provisions for students with particular dietary and lifestyle requirements, such
as separate dining areas and options for language education.

For both the Monols and the Uyghurs, an education system that emphasized
Mandarin meant that in order to succeed, students must learn Mandarin as their
primary language; however, in both cases, this was often at the cost of losing
their own culture. Somewhat ironically, by increasing their connection to the
Han group, it hurt their connection with their own group; Mongol stuents who
attended a special ethnic boarding school ``felt that it lowered their otherwise
equal social status with the Han and other ethnic groups''\footnote{ibid., 286}
and Uyghur intellectuals seeking to improve secular education and modernization
``struggle to preserve their Uyghur culture and language while maintining and
developing the ability to compete on a national level'' \footnote{Rudelson,
122}.

In addition to the negative effects of pushing the Mandarin language onto ethnic
minority students, the creation of special ethnic schools increased the
awareness of those groups, both within the groups themselves, and from the Han
that encountered them. A mixed Mongolian-Han boarding school saw that ``students
of each group formed a separate cultural circle, within which they
gradually built up mutual trust by sharing similar experiences of language,
ethnicity, and economic status''\footnote{Borchigud, 288}. Rather than building
cross-cultural connections, the mixed schools emphasized the differences between
ethnic groups, effectively alienating one group from another.

Among the Uyghur intellectuals, a split was created solely due to the
introduction of Mandarin-based education; students were permitted to choose
schools in either Uyghur or Han, resulting in the creation of separate cultures
within the intellectual class depending on which language one used throughout
school. Those who studied in Mandarin were viewed as not true Uyghurs, while
those who studied in Uyghur were considered to have recieved a poorer
education\footnote{Rudelson, 127--129}. This internal division would not have
existed if not for the ethnic eductation system imposed on the Uyghurs; even
though the literacy and success rates for students who studied in the Han
language increased, the conflict introduced into the region as a result bred
distrust and arrogance within the Uyghurs themselves.

Ultimately, though the Mongols and the Uyghurs are noticeably disparate groups,
they shared the experience of the effects of being defined as ethnic minorites
by the Chinese central government. The Han provided them with a system that
rewarded those who favored a pan-Chinese nation, as those willing to participate
in the educational and economical systems of the center would prosper, while
those who resisted found hardships. However, to accept that system meant
accepting an ethnic designation imposed from an outsider; this was an easier
thing for the Mongols, who had a unified identity on which that designation was
based, but still presents a problem to the Uyghurs, who are only developing
their identity as this proccess occurs.
