\section{The Disputes of Grey Areas}

\textit{10 February 2014}

An examination of boundary areas often provides insight into issues
that occur on one side of the divide or the other. The fuzzy
transitional zone between the grasslands used by mobile Mongolian herders and
China's stationary agricultural settlements is one instance of
such a space.  The physical landscape of that area is characterized by
a combination of constantly shifting ecological borders as the sand
dunes of the desert-steppe environment encroach onto arable farmlands.
This changing landscape created disparate ways of life that engendered
different cultural ideologies towards the usage of space. One group
was the pastoral nomads who valued the flexibility of
following the lands that provided for their sustenance; the other,
sedentary farmers whose carefully organized cultivation of the land
required a clear delineation of the world around them. Ultimately, the
proximity of these two disjoint cultures demonstrated some of the
problems that came from such an adjacency.

The Han had a sense of space that defined emptiness as a
negative concept \footnote{Williams, 671-672; connotations of the terms `huang', `ye', etc.}, an attitude that was
reflected in the very language they used to refer to bounded versus
unbounded areas. As a civilization that frequently needed to defend itself
against invading forces, they developed a culture of maintaining walls and
explicit boundaries in order to better identify the
separation between themselves and some sort of other. Since it is difficult to
fight against the nebulous and unbounded void, empty space became a
fearful object, something that the Chinese needed to harness and
tame in order to maintain control over their borders, both physical and
psychological. As a result, the very existence of delineated space
became a marker of Chinese sovereignty, reflected in highly structured
urban planning, border defense, and agricultural practice.

As a result of  these deep-seated needs for the explicit delineations
of space, unbounded territories seemed intolerably disorganized to the
Han; disorder meant a lack of control, a lack of control meant
unproductivity, and unproductivity was wasteful.  Thus, they saw the
unmodified grasslands to the north as an area of
waste, but also containing potential, capable of conversion to productive work through a
process of land cultivation and the civilizing of its inhabitants.
Regardless of the actual usage of that land, the Han needed to
organize it into something that they recognized as valuable.

Furthermore, the fact that such wasted land was occupied by other
peoples proved a challenge to the Han. It was difficult for them to
view the nomadic Mongols as anything other than aimless wanderers of
the grasslands, taking up space that could otherwise be put to better
use if they instantiated a systematic cultivation of the area. Since the
herders were benefiting from land that they had not worked to
cultivate themselves, the Han saw their existence as an affront to their values
of labor \footnote{Williams, 672--673; discussion the Han ecological
identity}. In other words, they thought of the Mongols as primitive,
lazy squatters, and the way to fix this problem was to impose order
onto the
chaos by organizing the wandering nomads into a structure that could
produce measurable amounts of work. Through this structure, the
Chinese sought to demonstrate their status as a more modern, developed
civilization, bringing all people under its rule into a high standard
of organized and productive living.

From those attitudes, the Chinese government made a series of policy decisions to
impose a Han-centric sense of structure and organization onto the
northern grasslands region. The primary effect of these policies was to
decollectivize the Mongol way of life; where the herders once shared
the open grasslands as one continuous area, the land was instead
divided into discrete parcels.  An enclosure policy was instituted to
prevent livestock from grazing freely on areas that the Chinese
agricultural scientists identified as vulnerable to erosion, as well as provide a system to track the work value of each parcel. 
The smaller plots of land could, in theory, be more easily monitored
for levels of productivity and stop potential damage resulting from
overgrazing of the grassland. Livestock and plots of land were then assigned
to individual households depending on the number of animals a
particular plot could support, and families were given incentives to adhere to
these boundaries \footnote{Williams, 680; enclosure policy details}.

As part of the enclosure policy, households that were more productive
were given subsidies by the central government. Though the subsidies
were intended to encourage adherence to the new order of cultivation,
they had the side effect of creating a wealth gap, as families that produced more could
buy more fencing materials, secure their own plots against their
neighbors' livestock, and let their own animals graze on unsecured
land. So, the policy in practice allowed households to enclose their
land to stock up good grazing areas, saving that grass for when the
rest of the pastures grew thin. In addition to causing more land
erosion by allowing the open grazing that the enclosure policy was
supposed to restrict, feuds often resulted from disputes over unclear property lines and
animals that strayed too far into the wrong plot \footnote{Williams, 684--685; some of the practical responses to the appearance of fences}.
Eventually, earning work points and subsidies became the main motivating
factor for the Mongol herders who wanted to survive
; in order to protect
their own interests, each household had to find ways to be more
productive than their neighbors, rather than tend to their flocks in the cooperative traditions.

Clearly, such sweeping changes could not have happened without resistance, as was
demonstrated by the students in \textit{Wolf Totem}. They grew to sympathize
with the Mongol way of life and lamented its destruction by Chinese
policies. When the main characters returned to the grasslands after being
away for thirty years, they were struck by the changes of the landscape when they saw
fenced-off and untouched grass pastures, dried rivers, and
ragged-looking animals \footnote{Jiang, 507--511 of \textit{Epilogue}}.
The effect of the enclosure policy was obvious to them; parcelization of the
land had disrupted the normal grazing patterns that had allowed the
grasslands to remain sustainable. Chen commented bitterly on the
transformation and noted the short-sightedness of sacrificing the land
for a quick economic boost, since he understood that ``the grassland could not return even if
the subsidies continued for the next century.'' \footnote{Jiang, 510} In their time  of living with the Mongols, they knew that the survival of the grass was the key to the survival of the people, so when the land suffered, so did its inhabitants.

Beyond the ecological disruption that Jiang's characters condemned,
they witnessed a cultural shift that came from the imposition of the
new Chinese order. As youths, they drew a parallel from the differences
between Mongol and Chinese horses to the differences between Mongol and
Chinese society. Even though they were Chinese from the city, they
recognized and valued the spirit of the Mongol horses, which they
considered an untamed
strength that could defeat even the greatest acts of labor. They called
the Chinese workhorses ``stupid'', and regarded them as slaves that could
only work and provide service to their masters, ultimately unable to defend
themselves from abuse; these characteristics quickly became a
reflection of the Chinese people who raised those horses
\footnote{Jiang, 305--306; in a conversation between Yang, Chen, and
Zhang as they observed horse mating fights}. When they returned to the grasslands thirty years later, they
found great disappointment in the fenced pastures. ``In the past,
who would dare build a fence on a grassland famous for its Ujimchinn
warhorses?'' asked Chen \footnote{Jiang, 510}. The irony was that they
once believed that the spirit of the Mongol warhorse could overcome any
attempts of domestication into a sedentary, labor-based lifestyle, but
the wild horses of their youth had been wiped out by modernization. 

Though a work of fiction cannot be relied upon as a statement of
historical accuracy, observable cultural damages and practical
ecological disruption did result from the act of
decollectivizing the northern grasslands. These were highlighted by some of the
ramifications of enclosure policies on the grasslands; instead of
keeping livestock confined to specific grazing areas, herders used
enclosures to preserve the pastures assigned to them and allowed their
livestock to overgraze unenclosed areas into severe erosion
\footnote{Williams, 680--681; noting the expansion of fenced land
versus large herds overgrazing unfenced land}. Additionally, the power imbalance
created by introducing subsidy incentives allowed some families to
prosper and
others to fail, and generated conflict and disputes over property
boundaries between groups that would otherwise have lived in peaceful
cooperation \footnote{Williams, 684; notes on violent incidences regarding fences}. These issues were compounded by the drastically different cultures attempting to survive on the same piece of land, as their incompatible ideologies made it difficult for them to reconcile their respective needs.

Despite the numerous problems caused by Chinese policy decisions
regarding the use of the northern grasslands, it is difficult to see whether or
not there were other options to address the needs of the Han society. The
Chinese could not tolerate a grey area that was neither clearly Mongol nor Han,
thus Inner Mongolia had to be brought into the Chinese status quo
in order to satisfy the Han cultural preference for clearly delineated spaces. Although
the landscape itself was a shifting environment, because it was a
Chinese territory, the people there needed to function with the Chinese
way of life, which meant highly organized agricultural practices, fenced plots, and measurable work.

Ultimately, the practical needs of a growing population required more
land dedicated to producing food and
resources; the steppes were seen as an area that could provide for the
Chinese, if only it could be tamed and organized. The proximity of
Beijing to the steppes region meant that the central government was very
much affected by the ecological changes of the Gobi Desert; continual
desertifcation and destruction of the northern farmlands presented
noticeable problems to the Chinese, from raging sandstorms that
buffeted the capital city to wide-ranging droughts that starved their
crops. The preservation of as much farmland as possible was crucial to
their survival. This necessitated agricultural
practices that could be measured, studied, and adjusted according to a
strict scientific rigor. Things could not be studied unless they were
held in place and monitored, thus the enclosure policy presented an
implementable solution to move the region into a more modernized status.

