\section{The Immigrant Ethic and the Spirit of Escapism}

\textit{14 December 2014}

At the core of Americanism is a dream, described by James Truslow Adams as the
belief that all people have the capacity for self-fulfillment\footnote{Adams,
404}. This is an ideal built out of the demands a culture places on itself when
one of the parameters of its founding is to choose to escape from an
unacceptable lifestyle and take on the risks that come from plunging into the
unknown. It is a paradoxical belief that still manages to sustain itself,
because its very structure dictates that to reject it is to reinforce it.  In
short, the American Dream is a self-propagating concept that rewrites the fear
of failure into the desire for success.

In the 1990 Nintendo game \textit{Super Mario World}, each level is a linear
maze with an explicit entrance and exit. Some levels have secondary exits that
require the player to notice an abnormality in the map and exercise some
creativity to exploit it. Towards the end of the game, though, one of the key
levels breaks this model; the obvious exit does not unlock any forward progress,
and there are no visual clues to hint the location of a secondary exit. The only
way to move beyond this level is to fly far off the edge of the screen, out of
the visible playing field, and wait to land on a small island that contains a
hidden door.

At age eight, I had little ability to deal with this; I only found the secret
exit because someone who watched me struggle with the level insisted I try
flying off the screen. ``If you die, you die, so what do you have to lose?'' I
was assured, and I followed those instructions because my only other choice was
to fail to beat the game. Later, I understood that this approach was what
immigrants, including my own parents, needed to believe in order to stake
everything on their dreams and start a life in a new world.

Prior to the founding of America, Benjamin Franklin already presented a success
story---arguably, the first great American success story. His timeline is one
that glorifies working ceaselessly, whether or not he even did the same himself.
That narrative of declaring one's starting circumstances as undesirable and
finding the means to escape is one that has been repeated and romanticized
through countless historical figures and fictional heroes in American lore. It's
an obsession that stems from the subtext presented in Franklin's way of
life---it's not just that working hard is the true path to success, but that it
requires a preceding step: first, you must choose to change your circumstances.

Obviously, not everyone makes that decision, or at least not at the magnitude
that Franklin did. It is simple to come up with an explanation; most people fear
failure, described by Sennott as ``the most uncomfortable phenomenon of
American life''\footnote{Sennott, 183} in his study of problems imposed by
American class divisions, and most people do not experience a level of
desperation in their lives that is sufficient to demand change.  However, this
just emphasizes the effects of those who do decide that the only way forward is
to stake everything on a leap of faith.

Such a drastic decision fuels the momentum of immigrants, who are perhaps a
stronger product of this Dream than those with much longer generations' worth of
history tied to America. Regardless of their originating culture, the immigrant
narrative shares a common thread: failure is an impossibility, because it is
simply not an option to not make it in the new world. You fly off the edge of
the screen, or you die trying. Immigration is a radical form of escapism, a
nuclear decision to up sticks and start over in a place that categorically
\textit{must} be an improvement. With that much at stake, there is no looking
back.

The assertion, then, is that by choosing to escape, one must have already chosen
success. This is clearly not an objective fact---the possibility of failure is,
of course, always there. However, once the stakes become high enough, it's no
longer meaningful to consider outcomes of failure, because only success matters.
Specifically for immigrants, the conditions of success lay in establishing a
secure life outside of their originating country, which means that failure
results in returning to the old country; by deciding to immigrate, the decision
has already been made to never fail. It's a redirection of the terms of success
outlined by the status quo that means as long as you never return, you've made
it. This is the step that counteracts the anxiety Sennott ties to the American
view of failure\footnote{ibid., 183}; when failure has been removed from
consideration, the only paths in view lead to success.

As a culture founded on escapism, the value system shifts from outcomes to
actions. If failure is removed from view, success as a concept loses meaning as
well. Since it's always a possibility to throw everything out and start over,
people must then derive value from something other than the results produced by
work; an unavoidable fact is that there is always work, so why not base a value
system on the work itself, rather than its products? Performing work is an
expression of agency; making choices is an expression of freedom.
What comes afterward is immaterial, because the process of those actions in and
of themselves reinforces their value. In other words, it no longer matters where
you go in life, but how you get there.

Thoreau says of a life, ``meet it and live it; do not shun it and call it hard
names. It is not so bad as you are''\footnote{Thoreau, 290}. He bases the value
of a life on how it is lived, not what it achieves, a conclusion he draws only
by rejecting the standard success model of the status quo and searching for a
more reliable path of self-fulfilment. This model of escapism is no different
from Franklin's, only it dictates working exactly as much as one should, not to
excess.  The immigrant ethic is to speak Franklin, while living Thoreau.

This is the nature of the American Dream. It is a dream that demands a constant
challenging of circumstances, even if such circumstances were a direct result of
pursuing the dream itself. A doctrine that requires rejection of itself as a
core tenet can only persist through this state of self-denial; a cultural
rejection of unfavorable circumstances similarly self-perpetuates through the
ideals formed by the desire to escape.
