\section{The Fear-Cult of Mao}


The disastrous conditions in China following the Great Leap Forward threatened
Chairman Mao's position as a leader of a revolutionary state. Sensing a
potential for loss of faith in his authority, Mao needed a way to secure his
status; the uncertainty the rest of the country had in China's future was turned
into a culture of paranoia through Mao's exaggeration of his own fear. He was
pre-emptively trying to root out potential betrayals within his own officials
before this happened, which meant that it no longer sufficed for his policies to
address actions; rather, his tactic was to create categories and terminology
that meant people could have incorrect thoughts and incorrect personalities,
going beyond just someone's personal history. By externalizing his own mistrust
onto the rest of the country, he created an environment in which he could never
be wrong, while making it impossible for anyone else to be right.

Many of the techniques used during the Maoist campaign were extensions of
procedures already in place prior to the Cultural revolution. The basic
format was that one would be identified as having performed some bad action,
required to make a self-criticism, and then accepting punishments in order
to correct that behavior. As part of Liberation, this process was crucial
for the Communist Party to gain control over an entrenched old class system.
This was such an effective means of establishing a status quo that it was an
obvious tactic to continue for Mao's personal authority campaign.

One of the main benefits of the self-criticism process was that party
members themselves were already expected to use it; in her family
biography, Jung Chang mentions multiple times when her father and
mother, both high-ranking Party members, had to perform a self-criticism
in order to address actions they had taken that were taken to be not
purely beneficial to the revolution. Through leaning on this familiar
process, Mao's campaign of fear easily percolated through the party;
self-criticism was always the right thing to do whenever there was a
problem, and thus if Mao wanted you to self-criticize something, it was
surely something that needed to be done.  Similarly, if someone did not
want to self-criticize, they would be in the wrong.

Mao targeted people he claimed were taking the “capitalist road”,
which suggested that they were people who were not yet capitalists,
but seemed to be heading in that direction. By defining his enemies
in such a vague, transitional state, that label had the flexibility
to cover virtually anyone it was applied to, except for Mao himself.
Esherick interprets this as having “implied that the accused wished
to reverse the achievements of China's socialist revolution” (283);
in other words, the capitalist road led away from Mao, and anyone
who walked down that path was a traitor to the Communist Party. The
problem, though, is that there isn't a literal road, and that
traitors are not so easy to identify; Mao had to criminalize the act
of considering treason if he wanted to prevent it from happening.

The critical factor in this is that Mao did not trust anyone, so
he needed to create an environment when other people didn't
trust each other, either. Chang claimed that Mao wasn't even
sure what a “capitalist roader” was (276), but that he knew they
existed and needed to be wiped out. His declaration of war
against an undefinable category of people resulted in his
loyalists scrambling to find those enemies, which meant that
they were practically inventing definitions on the fly. This was
a process of challenging previous structures of leadership, a
constant questioning of authority that was well-suited to the
teenagers and young people who were caught up in the excitement
of having a revolution. The Red Guard formed as an extension of
Mao's fear of enemies within the party, amplified by the common
adolescent mistrust of adults.

The categories that the Red Guard divided people into
reflected ideas that were already a part of the
revolutionary culture; people were “red” if they were
revolutionaries, “black” if they were counter-revolutionary,
and “grey” if they were ambiguous (Chang, 294). While these
categories started out from specific family backgrounds and
occupations, they rapidly drifted into more vague
definitions; anyone could be called “black” if they were no
longer in the favor of the “reds”. Furthermore, Mao's
insistence that a certain percentage of
counter-revolutionaries existed meant that the “reds” felt
the pressure to fill a particular quota, which motivated
them to label people as “blacks” just for the sake of
fulfilling Mao's claim. The vagueness of the red/black/grey
categories meant that people could be classified for reasons
from personal vendettas to purely random whims.

As the Red Guard considered themselves an extension of
Mao's will, they believed that Mao could not possibly be
wrong, and thus they could not possibly be wrong,
either. Slogans cited their support of Mao's absolute
authority, and they accepted even his apparent
contradictions in ideals. However, this mindless
mass-adherence to one man created opportunities for
disillusionment; even if it was impossible to resist the
tide of red, individuals were able to see through the
cracks and question whether or not this was the right
thing to do. Chang tells of times she did not wish to
participate in the destruction the Red Guards expected
her to join, even though she signed up willingly (293,
307). Esherick tells of Binbin, who joined a youth work
team when her father was under Red Guard detention, and
quickly learned to undermine the system by deliberately
breaking rules and then self-criticizing for a lenient
punishment (290-291). 

A culture based on paranoia can only go so far;
while an effective short-term means of upsetting the
status quo, the inevitable effects of the Cultural
Revolution was breeding discontent and even stronger
mistrust of Maoist policy in the long run. Mao's
tactic of making vague statements about broad
categories of enemies with no possibility of clear
distinctions meant that no one could truly
understand what he wanted; this ultimately ended up
damaging his credibility and creating a chaotic
environment of uncertainty.

