\section{The Adaptable Prosper}

\textit{20 March 2015}

China in the early 20th century was a chaotic period, especially for the
intellectual class of the late Qing dynasty. The Confucian system that preserved
a national sense of stability had crumbled, leaving a wake of abandoned
ideologies and ambiguous institutional structure. As traditional expectations
for success and prosperity proved unsustainable, some members of the former
elite turned to business ventures as a means to survive. However, the world of
capitalism is a much different one than the feudal system of the Confucians;
those who could adapt to the rapidly changing order were more likely to make it.

The collapse of the Qing dynasty was, in part, an effect of foreign influence
which destabilized the interior. Most of this influence came in the form of
trade, which brought with it strong pressures to modernize and accept a more
global economic order. We can witness this by observing the trajectory of the Ye
family branch in Tianjin, as Esherick describes changes in that city as a treaty
port\footnote{Esherick, 120}. Between the establishment of foreign concessions,
rapid development of modern public infrastructure, and heavy commercialization,
Tianjin became an area well-suited for incubating the new Chinese businessmen.
Ye Chongzhi was thus placed in an ideal position for this transition, due to his
previous experiences in industrial management and his convenient location for
accessing economic and trade centers. Perhaps he sensed that the instability of
the government would not provide him a sustainable career, and thus made ``the
provident decision to abandon politics for business''\footnote{ibid., 124}. In
the early 1900s, with frequent connections to outside affairs, Ye Chongzhi got a
head start on the sort of adaptations the rest of China would have needed to
make.

Further inland in Shanxi, the effects of modernization moved a little slower,
but were still noticeable. In 1913, Liu Dapeng gave up his teaching position and
entered the more profitable coal mining business for the sake of being able to
support his family\footnote{Harrison, 113--114}. Despite the fact that the
Confucian-based system of the Qing era had constantly let him down, though, Liu
approached doing business with the same moral code that carried him through his
past failures. He frequently took on mining ventures out of a sense of altruism
and good will, as evidenced in his takeover of the Shimen mine in order to help
a struggling family turn some profits\footnote{ibid., 118--119}. Members of the
community knew they could rely on him for being honest and trustworthy,
attributes that were critical for developing and maintaining a positive
reputation in an otherwise chaotic political and economic
environment\footnote{ibid., 122--123}.

Despite his earnest approach to business, there were many changes outside Liu's
control that made it difficult for him to prosper. Outrageous taxation became a
heavy burden in Shanxi, especially as local politicians started vying for more
power and leaned on local residents to support their
campaigns\footnote{ibid.,131}.  Technological advances in mining equipment made
a mess of the mountainside and cause the economy to favor large commercial
ventures, rather than the smaller pits that Liu was involved
with\footnote{ibid., 134}. In the face of these changes, Liu held on to his
strong moral code, as this integrity was the only thing he knew; he was thus
unable to adapt to the heavily profit-based biases of the mining business, and
slipped further into poverty over the next couple of decades\footnote{ibid.,
135}.

By the 1930s, we see an entirely different approach to doing business in China.
The Rong family, which established numerous textile and flour mills just before
the outbreak of war, demonstrated a wider range of adaptability to changing
political structures and economic pressures. This adaptability, above any other
strong ties to particular ideals, was what allowed them to persist through an
otherwise turbulent period. Early on in their ventures, they noticed that
battles with the Japanese near their factories in Shanghai threatened their
business; they keenly observed the effects of foreign presence, and counted on
the fact that their properties near the concessions would be
protected\footnote{Coble, 115}. Once the fighting ended, patriarch Rong
Zongjiang clearly recognized that the Chinese government would not protect them,
as evidenced by his formation of a merchant alliance that eschewed ties to any
political entity\footnote{ibid., 116--117}. His bold statement that ``China is
virtually a nation without a government''\footnote{ibid., 117} showed how little
faith he had in politics to protect the well-being of the people.

This divorcing of the family business from national loyalties goes further than
just forming an organization exclusively to protect commercial interests. After
Shanghai fell to Japanese forces in 1937, the Rongs registered their mills as
foreign American and British ventures, relying on an alliance with entities that
the Japanese did not yet wish to disturb. After Pearl Harbor, this alliance was
no longer valuable, and in fact made those mills more of a target; the response,
obviously, was to revert to Chinese registration to attempt a resistance against
Japanese seizures\footnote{ibid., 125}. Although that action failed to prevent a
Japanese takeover, it showed the Rongs' willingness to have a flexible national
affiliation for the sake of protecting their bottom line. Ultimately, they
regained control of their mills by going along with Japanese efforts for
economic cooperation, essentially playing to their desires for Pan-Asian
unification\footnote{ibid., 127}.

Beyond a flexibility in political dealings, the Rong family also played to
fluctuations in economic demand to maximize potential for profits. During the
decline in national production due to the war, they reduced  loss of profits by
running their equipment in small rural productions, which gave them the benefit
of being able to evade government regulations that larger operations were
subjected to, while also granting them access to raw materials when foreign
imports slowed\footnote{ibid., 130}. Their mills in Wuhan prospered during the
war because they were able to secure good local sources for cotton and wheat,
combining the output from both their textile and flour mills to provide
much-valued bags of flour at a time when finished products were highly
desirable\footnote{ibid., 133}. Through such methods of commodity hoarding and
playing to the fluctuating desires of the market, the Rongs managed to survive
through the hard times of war, while less profit-driven ventures were unable to
keep up.

In studying the Rongs' administration of their business, we find little evidence
of the Confucian value system of loyalty and avoidance of wealth-gathering that
dominated the previous generation of Liu Dapengs and Ye Chongzhis. While much of
the Rongs' success through that period was a result of the larger scale of their
enterprises and a good amount of luck, their willingness to adapt their business
practices to do whatever it took to survive played a non-trivial role in
allowing them to prosper. During a time when old systems have failed and new
systems have yet to take root, adaptability triumphed over tradition.
