\section*{References}


\bibent Buckley, Ralf. 2010. \textit{Conservation Tourism.} CABI: Oxfordshire,
UK.

\bibent Nyiri, Pal. 2006. \textit{Scenic Spots: Chinese Tourism, the State, and
Cultural Authority.} University of Washington: Seattle, WA.

\bibent Shapiro, Judith. 2001. \textit{Mao's War Against Nature.} Cambridge
University Press: Cambridge, UK.

\bibent Weller, Robert. 2006. \textit{Discovering Nature: Globalization and
Environmental Culture in China and Taiwan.} Cambridge University Press:
Cambridge, UK.

\bibent Buckley, Ralf. 2010. \textit{Conservation Tourism.} CABI: Oxfordshire,
UK.

\bibent Ghimire, Krishna B. and Li, Zhou. 2001. ``The Economic Role of National
Tourism in China.'' \textit{The Native Tourist: Mass Tourism Within Developing
Countries.} Earthscan Publications: London, UK.

\bibent Grusin, Richard. 2004. \textit{Culture, Technology, and the Creation of
America's National Parks.} Cambridge University Press: Cambridge, UK.

\bibent Huang, Wen. 2014. \textit{Tianzhushan Global Geopark}. Tianzhushan
Geopark Management Committee. \url{http://english.tzsgy.com/Culture.asp?Id=1000}
(accessed 6 April 2015).

\bibent Huntley, Jen A. 2011. \textit{The Making of Yosemite: James Mason
Hutchings and the Origin of America's Most Popular National Park.} University
Press of Kansas: Lawrence, KS.

\bibent Nyiri, Pal. 2006. \textit{Scenic Spots: Chinese Tourism, the State, and
Cultural Authority.} University of Washington: Seattle, WA.

\bibent Sofiel, Trevor H.B. and Li, Fung Mei Sarah. 2003. ``Processes in
Formulating an Ecotourism Policy for Nature Reserves in Yunnan Province,
China.'' \textit{Ecotourism Policy and Planning.} CABI Publishing: Trowbridge,
UK.

\bibent Weller, Robert. 2006. \textit{Discovering Nature: Globalization and
Environmental Culture in China and Taiwan.} Cambridge University Press:
Cambridge, UK.

\bibent UNESCO, 1998. \textit{State of Conservation Reports}. Ref:
WHC-98/CONF.203/8

\bibent UNESCO. 2002. \textit{Wulingyuan Periodic Report}.

\bibent UNESCO. 2013. \textit{Yosemite National Park Periodic Report}.

\bibent UNESCO. 2015. \textit{Tianzhushan}. Ref: WHTL-5992.
