I think of my post-bacc phase as this: one day, several years after I finished
my bachelor's in creative writing, I realized I missed writing papers, and
regretted not engaging with paper-writing in a more meaningful way during my
undergraduate years. I graduated from the English department! How did I fail to
feel satisfied with my paper-writing? (the answer probably remains obscured by
the stale beer-sweat of my post-adolescent angst.) Fortunately, for the sake of
my unfulfilled desires, it was trivial to register as a non-degree student at my
alma mater.

It always seemed a little unfair to the other undergraduates when I was doing my
post-bacc coursework. Not only had I already completed a bachelor's degree, but
I did it at the same university as they were attending. I had little at stake,
with far less work on my plate. I was hitting far below my weight class, and I
knew it, and sometimes they knew it. I mean, I've always been a shameless
over-achiever and an incorrigible teacher's pet.

So, maybe it's time to move on. I'm writing this now as part of my transition
into my pre-doc phase: the period of time during which I have not yet applied to
a graduate program, but I'll be taking graduate-level courses and producing more
serious work.

As a pre-doc, the main difference is that my classmates will have achieved
things I haven't yet reached: they've taken their GREs, they've applied to a
graduate program, and, more to the point, are actual doctoral candidates. Me?
I'm still just a non-degree staffer filling up my free time with busywork.
What's that going to feel like? I guess I'll find out! Also, now I'll have to
pay tax on my tuition benefits (boooo).

This is an archive of my rampage through Carnegie Mellon University's history
department from 2012--2016, courtsey of my staff tuition benefits. These are
presented in chronological order, with one chapter per course. I've made a few
minor typological and typographical edits for the sake of consistency, but other
than that, these essays remain the same as what I turned in to my professors.

\textit{---5 January 2017; Pittsburgh, PA}
