\documentclass[12pt]{article}
\usepackage{mla}
\begin{document}
\begin{mla}{Vincent}{Zeng}{Professor Scott Sandage}{79-245 Capitalism and Individualism}{\today}{The Bootstrapping
Factor} 
	Max Weber builds a model of the particular flavor of American
	capitalism that depends on a baked-in sense of duty, that all should
	adhere to a divine order for everyone to fulfill his potential and duty
	towards an economically-viable calling. I argue that he's missing a key
	point in his analysis: \textbf{a defining feature of the workaholic drive
	that separates Americans from other modern capitalist cultures is the
	feeling of necessity that derives from building something out of less
	than nothing.} This extends to the belief that failure is unacceptable,
	a lack of progress is tantamount to failure, and, in extreme cases,
	that failure can mean death. It is not only economics that motivates
	Americans to work harder than they are expected to, but a culture that
	develops out of being forced to pull themselves up by their own
	bootstraps, or die.

	If we remove money from the equation, Weber's framework collapses. When
	he credits the ``devotion to a `calling' of moneymaking''
	\footnote{Weber, p. 32} as a major factor in the successes of notable
	American cultural heroes, he neglects to understand that the
	moneymaking was only incidental to the way in which they conducted
	their lives. It happened to be that Benjamin Franklin, Andrew Carnegie,
	and others were \textit{highly talented} at generating massive
	quantities of wealth, but their deeper motivations came from a driving
	need for self-improvement.

	A better example illustrating the bootstrapping factor comes from
	examining Frederick Douglass's trajectory throughout his life. It
	wasn't until later in his life that money even entered into his
	calculus; prior to that point, he pursued a desire for self-improvement
	and knowledge acquisition before he even understood what implications
	and opportunities that would give him. He would not have realized the
	power of earning his own wages \footnote{Douglass, \textit{Narrative}
	p. 95--97} if he had never realized the possibility of being a free
	man. He would not have realized the possibility of being a free man if
	he had not learned to read \footnote{Douglass, \textit{Narrative} p.
	63--64}. He would not have learned to read if he did not get the sense
	that it would somehow \textit{improve} his status as a person
	\footnote{Douglass, \textit{Narrative} p. 60}. Because the events
	happened in such a sequence, it could not possibly have been an
	economic motivation that drove Douglass to better himself.

	As Douglass develops a further self-awareness of his own peculiarity,
	he recognizes that it was in fact his encounter with adversity that
	provided him the circumstances that made him more than what he was born
	into. He defines similar `self-made men' as ones who ``are obliged to
	come up...in open and derisive defiance of all the efforts of society
	and the tendency of circumstances to repress, retard, and keep them
	down.'' \footnote{Douglass, ``Self-Made Men'' p. 550} Money had nothing
	to do with it; Douglass \textit{had} to raise himself out of his
	circumstances because it was what he needed to do in order to survive.
	Progress, for him, meant life, while failure to progress would have
	killed him. In his case, it was quite literal; once his self-education
	progressed to a point at which he could no longer accept slavery as an
	option, he decided that he would rather risk the punishment of death as a result of striking back
	against a white man than allow himself the inhumanity of being whipped
	as a slave \footnote{Douglass, \textit{Narrative} p. 79}.

	Douglass doesn't credit only adverse circumstances for his success,
	though; he knows that his status as a black man and former slave means
	he had much more to work against \footnote{Douglass, ``Self-Made Men''
	p. 557}. For that matter, he identifies that great men are ones who
	work without regard to anything other than work \footnote{Douglass,
	``Self-Made Men'' p. 556, 560}, and the best way to incite work in an
	individual is to put him in a situation that seemingly prevents him
	from getting what he wants \footnote{Douglass, ``Self-Made Men'' p.
	558}. When he tells us that we should measure a man's success ``not by
	the heights others have obtained, but from the depths from which he has
	come'' \footnote{Douglass, ``Self-Made Men'' p. 557}, he wants us to
	acknowledge that the lower someone starts, the greater their path of
	accomplishment can be; it is not enough for a man to live with what
	life has given him, but that the \textit{process} of achievement shows
	more about his character.

	You could say that one of Weber's points is that the money itself is
	not the sole motivating factor for the spirit of modern capitalism
	\footnote{Weber, 20--21}, and thus I am deliberately skewing his
	argument, but his framework deals primarily with the sense that there
	is something about the economic pressure of capitalism as a strictly
	unavoidable part of one's environment \footnote{Weber, p. 18} that
	fostered the mindset we are trying to understand. I claim that he has
	oversimplified the problem; the driving force behind the spirit of
	capitalism is the need to create something out of almost nothing, and
	money just happens to exist as a metric by which we can measure the
	amount that one has succeeded. Douglass's life, while an extreme
	example of the bootstrapping factor, reflects a larger pattern of early
	American culture; in order to survive and prove themselves capable of
	existing as a legitimate nation, they had to overcome a lack of
	infrastructure and established roots that their European spectators had
	long solved.

\begin{workscited}

	\bibent
	Douglass, Frederick. \textit{Narrative of the Life of Frederick
	Douglass, An American Slave, Written by Himself}. Bedford Books. 1993.

	\bibent
	Douglass, Frederick. ``Self-Made Men''. \textit{The Frederick Douglass
	Papers}. Yale University Press. 1992.

	\bibent
	Weber, Max. \textit{The Protestant Ethic and the Spirit of Capitalism}.
	Roxbury Publishing Company. 2002.

\end{workscited}
\end{mla}
\end{document}
