\documentclass[12pt]{article}
\usepackage{mla}
\begin{document}
\begin{mla}{Vincent}{Zeng}{Professor Scott Sandage}{79-245 Capitalism and Individualism}{\today}{A Collective Dreaming}

The American Dream is a vague concept that combines an unavoidable
status quo with the expectation that anyone who manages to rise 
up from the crowd will achieve some sort of success. \textbf{In order for that Dream
to stand, a harmony must be struck between the ideal of universal
self-fulfillment and the practical needs of a collaborative society.}  We can
witness this struggle through the dramatization of fictional stories in which
characters who try to set themselves apart are mowed down for, ironically,
trying to achieve their version of the American Dream.  On one hand, we have
Edna Pontillier of Kate Chopin's ``The Awakening'', whose attempt to engage
with her discovery of the Dream from a position of its infrastructure ended in
failure; on the other, Linda Loman of Arthur Miller's ``Death of a Salesman''
presents us an option for a woman to succeed in a context where only the
achievement of men seem to matter.

For the purposes of this analysis, I will first clarify my usage of the words
`success' and `failure'.  In describing characters, I use these terms based on
their final states within the narrative work.  Specifically, I refer to Edna's
ending as a failure because in taking her own life, she has made it impossible
for her to ever achieve anything further.  On the other hand, I describe Linda
as having succeeded in that she survived the course of the play, and thus
her character is allowed the potential of progress beyond the narrative.  In a bit of
an oversimplification, we can also view either story as a morality tale,
through which the authors show us that characters live and die as a
consequence of how they choose to accept their places within the framework of
the American Dream.

As a concept, then, the Dream is something with both a theoretical ideal and a
practical reality.  The ideal is that all people shall achieve a status and
recognition based on the fulfillment of their human potential, as James Truslow
Adams defines in his historic analysis of the American condition
\footnote{Adams, p. 404}.  In reality, though, people still need to adhere to
some sense of social structure and organized positions, because there is no
guarantee that every person will always end up with both the potential
\textit{and}
desire to reach a state that allows them to exist harmoniously with other
people.  That framework forms a status quo in which all participants are
unavoidably involved; Chopin and Miller, then, explore the possibilities that
lay within individual human interactions with that framework.

With all this in mind, an obvious question appears: Why did Linda succeed,
while Edna failed?  We can examine how each author set up their characters; as
a narrative device, both characters started in a situation that seemed the
opposite of their result.  Edna was placed in a life designed to succeed, with
a husband more than capable of financially supporting her \footnote{Chopin,
p. 83 ``I'll let Leonce pay the bills''} \footnote{Chopin, p. 79, as Edna
describes the house and money as all belonging to her husband}, friends and
children that mostly adored her, and a support network of people to take care
of her immediate physical needs \footnote{Chopin, p. 83, the maid that comes
in to pick up a broken vase} \footnote{Chopin, p. 72, her mother-in-law and
quadroon take the children off her hands}. Linda, on the other hand, seemed
doomed to fail from the start, as her husband doesn't respect her
\footnote{Miller, p. 64--65}, their financial situation is in dire straits
\footnote{Miller, p. 54--56}, and both sons seem destined to be useless louts.

In both women's cases, though, they occupied a position within their context
as just part of the infrastructure of someone else's Dream; neither of them
were expected to engage in pursuits independent of their family unit's
best interests. At a superficial level, it seems as if the women of men were
excluded from pursuing the Dream at all, but I offer that the American Dream
is one that is pursued as a collective whole. The fulfillment of the Dream
depends on the strength of its framework, which means there is no room for
someone to step outside of their role.

This brings me to a secondary definition of `success' and `failure'; one who
succeeds has accepted their place within the American Dream, and works towards
filling just that potential and nothing more, while one who cannot accept
their position will ultimately fail in the process of trying to escape.
There's a bitter irony in this interpretation in that the Dream itself
encourages stand-out, individualistic pursuits, but for these two women
characters, their starting points are locked into place, and their only
freedom is to decide whether or not they can accept that.

We can answer the question posed earlier by taking both of these definitions
together; Edna, as the character who failed, did not accept that she must
exist as just another leg propping up a
society she could not even understand, while Linda allowed herself to become
the tireless supporter of the burden of a failing family. The irony of both
situations further highlights the tragedy of these women's roles within the
American Dream: Edna refused to accept her success, and thus she
failed; Linda unconditionally accepted her failure, so she succeeded.

If the heroic position is occupied by a man on the path to win at
life, women exist as part of the implicit infrastructure for the American
Dream. By allowing Linda to survive through the tragedy of Willy Loman, Arthur
Miller shows us that there is a way for women to succeed in the fulfillment of
the American Dream. Chopin shows us the other option, as
Edna's failure stems from the fact that she had entered into a position that
required her adherence to a framework that depends on its own
self-perpetuating existence. The American Dream is not one of individuals, but
one shared with everyone who dreams it, and it cannot support itself without
the cooperation of its component parts.
\end{mla}
\begin{workscited}
	\bibent
	Adams, John Truslow. \textit{The Epic of America}. 1991.

	\bibent
	Chopin, Kate. \textit{The Awakening}. Norton Critical Edition. 1976.

	\bibent
	Miller, Arthurh. \textit{Death of a Salesman}. The Viking Press. 1979.
\end{workscited}
\end{document}
